---
title: "Homework 1"
author: Zhixing Wu  (zw2709)
output: github_document
---

This is the solution to Homework 1

```{r}
library(tidyverse)
```


# Problem 1

Create a data frame with specified elements:

```{r create_df}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp >0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "med", "med", "med", "high", "high", "high", "high"))
  )

```


Take the mean of each variable in the data frame

```{r mean_pull-vari}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))

```

I can take the mean of numbers and logical, but not character or factor.


Then use as.numeric function
```{r try_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

We can get results for numbers, logical and even factor, but not for character.

```{r}

as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)

```

# Problem 2

This is infomation about the dataset.

```{r dataset_penguins}
data("penguins", package = "palmerpenguins")
summary(penguins)
```



### Variables
The dataset penguins has eight variables, and the variable names are `r names(penguins)`.



There are three factors in total: 'species','island', 'sex'.

* The variable 'species' has three levels: `r levels(pull(penguins, species))`.
* The variable 'island' has three levels: `r levels(pull(penguins, island))`.
* The variable 'sex' has three levels: `r levels(pull(penguins, sex))`.



The other five variables have numerical values.

* The variable 'bill_length_mm' has the range: [`r range(pull(penguins, bill_length_mm), na.rm = TRUE)`], the minimum value: `r min(pull(penguins, bill_length_mm), na.rm = TRUE)`, the maximum value: `r max(pull(penguins, bill_length_mm), na.rm = TRUE)`, the mean value: `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`.

* The variable 'bill_depth_mm' has the range: [`r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`], the minimum value: `r min(pull(penguins, bill_depth_mm), na.rm = TRUE)`, the maximum value: `r max(pull(penguins, bill_depth_mm), na.rm = TRUE)`, the mean value: `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)`.

* The variable 'flipper_length_mm' has the range: [`r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`], the minimum value: `r min(pull(penguins, flipper_length_mm), na.rm = TRUE)`, the maximum value: `r max(pull(penguins, flipper_length_mm), na.rm = TRUE)`, the mean value: `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

* The variable 'body_mass_g' has the range: [`r range(pull(penguins, body_mass_g), na.rm = TRUE)`], the minimum value: `r min(pull(penguins, body_mass_g), na.rm = TRUE)`, the maximum value: `r max(pull(penguins, body_mass_g), na.rm = TRUE)`, the mean value: `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`.

* The variable 'year' has the range: [`r range(pull(penguins, year), na.rm = TRUE)`], the minimum value: `r min(pull(penguins, year), na.rm = TRUE)`, the maximum value: `r max(pull(penguins, year), na.rm = TRUE)`.



### Size of the dataset: 
The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns in total.
The size of the 'penguins' dataset is `r nrow(penguins)` * `r ncol(penguins)`.


### Mean flipper length
The mean of flipper_length_mm is  `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

### Scatterplot
Create a data frame containing variables for the plot.
```{r variables}
plot_df = tibble(
    x = pull(penguins, bill_length_mm),
    y = pull(penguins, flipper_length_mm),
    species = pull(penguins, species)
)

```

This is the scatterplot of flipper_length_mm (y) vs bill_length_mm (x).
```{r scatterplot, warning = FALSE}
ggplot(plot_df, aes(x = x, y = y, color = species)) + geom_point()

ggsave('scatter_plot.pdf', height = 4, width = 4)
```


